%Group Report Information: Has this been done before? How? If not, what's the closest related device/prototype? Is there any novelty in your device? (It is not necessary that your device is novel) Did you use an existing project as inspiration or starting point??

\section{Background}
It is fair to say that a drawing machine is not a novel idea. There are a number of projects that is drawing on a vertical surface by pulling/releasing a line such as our machine. An example is a video found on Vimeo\citep{Vimio:2010:DrawingMachine} by Harvey Moon. It has two motors placed in the upper right and left corner of a whiteboard. Then a motor in each has a pulley structure on the shaft that may release/pull a line. This line from both motors connects a pen which by gravity is forced down.\\ Another project called {\texttt Hektor}, is  a spray can draw on walls in the vertical plane. The spray can is controlled by two stepper motors and with gravity forced down \citep{Hektor}. %Then there are 
3D printers, which is quite an inspiration, shows how stepper motors can be used to move a head in 3 dimensions. It would though be quite expensive to buy a smooth rod for this project.
\\\\
The above mentioned projects provides some inspirational material, however the Drawing Machine of ours is based on our own ideas, code and experience.  We did not seek inspiration for the project until writing this report. Ideas such as the pulley setup from Harvey Moon is something we could have stumbled upon earlier. It is an idea that might have improved the accuracy of the solution we ended up with.

